When does vapor pressure deficit drive or reduce evapotranspiration?

### 2018-02-19 doc/paper/vpd_et_paper.tex
got formatting up to snuff with GCB, now can really focus on finishin up the writing
okay, going ot do one last run of analytics to dot my i's and cross my t's, then will be done

\begin{keypoints}
\item = enter point 1 here = 
\item = enter point 2 here = 
\item = enter point 3 here = 
\end{keypoints}

@@

The Medlyn model for stomatal conductance has been shown to behave very well across PFTs, compared to other models from the leaf to ecosystem scale \citep[ZHOU ET AL AS WELL** ?? - Pierre says Zhou 2014][]{Lin_2015, Zhou_2015}. It is adapted at the ecosystem scale by multiplying $g_{l-s}$ by leaf area index (LAI) and converting units to m s$^{-1}$:

>>>>

\begin{keypoints}
\item Add given Medlyn (nature response) and Zhou2014 uWUE should increase roughly proportional to atmospheric CO2 concentration,
  so really the env VPD will be where plants will feel the effect of global warming stronges, b/c effect of CO2 cancels.
\item = enter point 2 here = 
\item = enter point 3 here = 
\end{keypoints}

@@

The Medlyn model for stomatal conductance has been shown to behave very well across PFTs, compared to other models from the leaf to ecosystem scale \citep[][** still unsure about citing Zhou here]{Lin_2015, Zhou_2014}. It is adapted at the ecosystem scale by multiplying $g_{l-s}$ by leaf area index (LAI) and converting units to m s$^{-1}$:
